---
title: An Example R Markdown Document
subtitle: (A Subtitle Would Go Here if This Were a Class)
author: | 
 | Mathew E. Hauer^1^ & Author^2^
institute:  | 
 | ^1^University of Georgia | ^2^University
titlegraphic1: logo-uga-color.eps
titlegraphic2: florida-state-university-logo.png
fontsize: 10pt
output:
 beamer_presentation:
    template: ../PRESENTATIONS/presentation_template.tex
    keep_tex: FALSE
make149: true

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

